Careers in Ruins: Academic Archaeology Job Trends From 2013 - 2023

### 2024-09-18 analysis/paper/paper.qmd
article qmd for the journal article

---
title: "Title Goes Here"
author:
  - Jane Doe:
      correspondence: "yes"
      email: janedoe@fosg.org
      orcid: 0000-0003-1689-0557
      institute:
        - fosg
        - fop
  - John Q. Doe:
      institute: fosg
      orcid: 0000-0003-1689-0558
  - Peder Ås:
      institute: fosg
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: Acme Corporation
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - fosg:
      name: Formatting Open Science Group
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

# Introduction

Here is a citation [@Marwick2017]

# Background

# Methods

# Results

<!-- Here's some example analysis code: -->

@@

ggplot(EEO_wordcount) +
  aes(word_count, year_ad_posted) +
  geom_histogram()

>>>>

---
title: "Careers in Ruins: Academic Archaeology Job Trends From 2013 - 2023"
author:
  - Ben Marwick:
      correspondence: "yes"
      email: bmarwick@uw.edu
      orcid: 0000-0001-7879-4531
      institute:
        - uw
  - Anne Marie Poole:
      institute: uw
      orcid: xxx
  - Ailin Zhang:
      institute: uw
      orcid: xxx
  - Setareh Shafizadeh:
      orcid: 0000-0003-2231-4310
      institute: uw
  - Jess Beck:
      orcid: 0000-0002-7387-2307
      institute:
        - ucd
institute:
  - uw: Department of Anthropology, University of Washington, Seattle, USA
  - ucd: School of Archaeology, University College Dublin, Ireland

title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 900
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |

keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

This document contains the code used to generate the figures for our SAA poster.

@@

ggplot(jobdata_requirements_means %>% 
         filter(name == "diversity\nstatement") ) +
  aes(year_ad_posted, 
      mean_n) +
  geom_col()
